Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2016-10-29 apj.tex
clean up for, should be ready for another collaboration release.

\begin{abstract}
An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
broadband photometry and their colors are found to be 
dependent on the spectral equivalent widths and the color parameters, to better than 
%-----
$(1-5\times10^{-5})$
%------
confidence.
The two color parameters exhibit the behavior expected from the two-parameter
\citet{1999PASP..111...63F} dust model, yielding a per-supernova scatter in
total-to-selective extinction.  The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
Extending the model to three color parameters gives almost identical results for
the two parameters
plus a detection of a third parameter at  $>98$\% confidence; this new parameter is responsible for supernova color diversity
beyond those tracked by the spectral features and two-parameter dust models.
\end{abstract}

@@

\subsection{Model}
We assume 
that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
on the
 equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
$EW_{Ca}$, $EW_{Si}$,
and $\lambda_{Si}$ the wavelength of the minimum of 
the SiII$\lambda6355$ feature:
these spectral features are associated with SN~Ia  spectroscopic diversity  
\citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
The explicit omission of light-curve shape in our model is compensated by its proxy
$EW_{Si}$ at peak brightness
\citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
$C_c$.  A grey magnitude offset, $\Delta$, is included for each supernova
to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
The observed magnitudes are linearly dependent on the
extrinsic-color parameters $k_0$ and $k_1$.  
The observables
$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $\lambda_{Si,o}$
shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
Unlike the parameters associated with
the spectral measurements, $EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$,  the latent
parameters $k_0$ and $k_1$ are not directly associated
with observables but are rather drawn from the set of peak magnitudes.
The model 
\color{red}
likelihood
\color{black}
is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} \\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si}  \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} \\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} \\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si}
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
The global parameters $c$, $\alpha$, $\beta$,  and $\eta$,  are the intercepts and slopes of the linear relationships that
relate intrinsic magnitudes with the spectral-feature parameters.
(In this article we freely interchange the parameter indices with  $01234$ and $UBVRI$.)
The global parameters $\gamma^0$, $\gamma^1$  are the slopes that connect the extrinsic-color
parameters to observed magnitudes.

@@

\color{red}
Recall that our model does not specify the color of a supernova that suffers no extrinsic effects, but rather sets the
mean of $k_0$ and $k_1$ of the distribution to zero.
There is an unconstrained $k_0^0$, $k_1^0$ that corresponds to an intrinsic supernova.  The true extinction is
$A^T_X(k_0,k_1)= A_X(k_0,k_1) -  A_X(k^0_0,k^0_1)$ where $A_X(k_0,k_1) =  \gamma^0_X k_0 + \gamma^1_X k_1$.
The true color excess is $E^T(B-V) = A^T_B-A^T_V$.
Despite this ambiguity, a linear slope relating the $E^T(B-V)$ and $A^T_V$ for a set of supernova is the same slope
relating $A_V$ and $E(B-V)$.
\color{black}
Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
which a linear fit gives a slope of $R_V=2.77^{+0.08}_{-0.09}$.
\color{red}
The full set of supernovae does not coincide with the expectations of a single linear law; the supernova population rather appears to be peaked
on a ridge line, and having a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
but can have values that extend toward lower values.

The quantity $R^F_V = A^F_V/E^F(B-V)$ for an individual supernova is unspecified without knowledge of the intrinsic color.
For a qualitative view, we choose the zeros for $V$-band extinction and color-excess such that the bluest supernova roughly correspond to $E(B-V)=0$,
$A_V=0$, and such that the ridge line is close to flat.
With this ansatz, we
estimate $R^T_V$ per supernova as shown in Figure~\ref{avebv:fig}, with the expectations of the
 \citetalias{1999PASP..111...63F} model for fixed $R^F_V$ overplotted.
With this choice of zeropoints, the ridge line corresponds to $R_V^F\lesssim 2.5$, and even lower values of $R_V^F$ below the ridge line.
We emphasize that the shape of the locus in this plot (though not the relative positions of the points)  and the flatness
of the ridge line is specific to our choice of zeropoints, and that our model does not specify the zeropoints.
A specification of per-supernova $R_V$ requires a model that can identify supernovae that suffer no extrinsic effects,
for example by modeling  a constraining distribution for the extrinsic parameters \citep{2016arXiv160904470M}.
\color{black}

@@

Until now we have considered $k_0$ and $k_1$ without association with any specific dust model, but they could be interpreted as
parameters of a single  dust model.
\color{red}
Plotted in Figure~\ref{avebv:fig} are the expectations for measured $A(V)$, $E(B-V)$, and $R^T_V$ for $R^F_V=1.1, 1.9, 2.5, 3.1$
within the context of the \citetalias{1999PASP..111...63F} model.
Note that for our broadband measurements, the relationship between $A(V)$ and $E(B-V)$ is subtly
non-linear, and $R^T_V$ is not constant, for a fixed value of $R^F_V$.
\color{black}

The \citet{1989ApJ...345..245C} dust law can be expressed as a two-parameter linear model
\begin{equation}
A_X = a(X)  A_V + b(X) E(B-V).
\end{equation}
The \citet{1999PASP..111...63F} (hereafter referred to as \citetalias{1999PASP..111...63F}) model is approximately described by a linear model with
the above form, with
$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.78\}$ and $b(U,B,V,R,I)=\{  1.64,   1.06,   0.16,  -0.40,  -0.52\}$ for the case of
$R^F_V=2.5$ and the updated
\citet{2007ApJ...663.1187H} SN~Ia template at $B$-band peak.  This linear approximation
is good in the ranges of $R^F_V$ and wavelength under consideration, in that these vectors vary by $<5$\% over the range $1.9<R^F_V<3.1$.

Our model can be expressed as
\begin{equation}
A_X = \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V).
\end{equation}
Our best-fit values for the $\gamma$ coefficients (from Table~\ref{global:tab}) can expressed in terms of the $a(X)$ and $b(X)$ vectors:
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} 
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
1.22 & 2.75 \\
0.81 & -5.50
\end{array}
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\begin{pmatrix}
\vec{\epsilon}_a \\
\vec{\epsilon}_b
\end{pmatrix},
\end{equation}
where the two residual $\vec{\epsilon}$ vectors are perpendicular to both $a(X)$ and $b(X)$ and
contribute  3\% and 4\% respectively to the total  length of the $\gamma$ vectors.
This result indicates that
the allowed variation of $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are almost identical.

@@

Data of SN~2014J are  analyzed using our model and using the parameter values found with the SNfactory sample.
The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
following their prescription of averaging measurements within 5-days of peak $B$ magnitude.
Their values 
$E_o(U-V) =   2.23 \pm   0.03$,
$E_o(B-V) =   1.28 \pm   0.04$,
$E_o(R-V) =  -0.47 \pm   0.03$,
$E_o(i-V) =  -0.92 \pm   0.03$
are plotted in Figure~\ref{sn2014j:fig}.
\color{red}
The central wavelengths of the filters are 3660, 4280, 5350, 6310, and 8100 \AA\ respectively, in contrast to the central
wavelengths 
3640, 4390, 5290, 6370, 7680 \AA\ of our synthetic bands.  With the approximate correspondence between the filter sets,
\color{black}
these data are fit to the model
\begin{equation}
E_o(X-V) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)x_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)x_1,
\end{equation}
where we use the median values of the $\gamma$- and $\delta$-terms from Table~\ref{global:tab} and the fit
parameters $x_i $.

@@

The best-fit parameters for SN~2014J are 
%----
$x_0= 2.65$, $ x_1=-1.64$ with covariance
%----
\begin{equation}
\begin{pmatrix}
\begin{array}{rr}
0.048 & 0.047 \\
0.047 & 0.248
\end{array}
\end{pmatrix}.
\end{equation}
The predicted values of observed $E_o(B-V)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
overlap with the data within the error bars.   For comparison, the best-fit model determined by  \citet{2014ApJ...788L..21A} model using
UV through NIR data,
a  \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$
\color{red}
is shown in their Figure 3.
\color{black}
Our model predictions provide a significantly better match to the data.

@@

\subsection{Improving SNe~Ia as Standard Candles}
The model and results presented here
carry information on the calibration of absolute magnitude.  The grey parameter $\Delta$ represents Hubble residuals after
application of the model, and its  $0.10$ mag dispersion has contributions from intrinsic dispersion, peculiar velocities, and
measurement uncertainties.
\color{red}
The purpose of this analysis was designed to mine information from the SNfactory data set, and so the results presented here
are specific to it both in terms of its population distribution and potentially noise.  This is the approach taken by previous
exploratory work.
A new analysis that explicitly measures out-of-sample performance is required to robustly determine how
well the addition of third parameter inferred from supernova magnitudes can be used to measure supernova distances.
\color{black}

>>>>

\begin{abstract}
An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
broadband photometry and their colors are found to be 
dependent on the spectral equivalent widths and the color parameters, to better than 
%-----
$(1-5\times10^{-5})$
%------
confidence.
The two color parameters exhibit the behavior expected from the two-parameter
\citet{1999PASP..111...63F} dust model.
The derived dust law is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
Extending the model to three color parameters gives almost identical results for
the two parameters
plus a detection of a third parameter at  $>98$\% confidence; this new parameter is responsible for supernova color diversity
beyond those tracked by the spectral features and two-parameter dust models.
\end{abstract}

@@

\subsection{Model}
We assume 
that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
on the
 equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
$EW_{Ca}$, $EW_{Si}$,
and $\lambda_{Si}$ the wavelength of the minimum of 
the SiII$\lambda6355$ feature:
these spectral features are associated with SN~Ia  spectroscopic diversity  
\citep{2006PASP..118..560B, 2008A&A...492..535A, 2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
The explicit omission of light-curve shape in our model is compensated by its proxy
$EW_{Si}$ at peak brightness
\citep{2008A&A...492..535A, 2011A&A...529L...4C}. 
Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
$C_c$.  A grey magnitude offset, $\Delta$, is included for each supernova
to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
The observed magnitudes are linearly dependent on the
extrinsic-color parameters $k_0$ and $k_1$.  
The observables
$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $\lambda_{Si,o}$
shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
Unlike the parameters associated with
the spectral measurements, $EW_{Ca}$, $EW_{Si}$ and $\lambda_{Si}$,  the latent
parameters $k_0$ and $k_1$ are not directly associated
with observables but are rather drawn from the set of peak magnitudes.
The model 
\color{red}
likelihood density
\color{black}
is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} \\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si}  \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} \\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} \\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si}
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
The global parameters $c$, $\alpha$, $\beta$,  and $\eta$,  are the intercepts and slopes of the linear relationships that
relate intrinsic magnitudes with the spectral-feature parameters.
(In this article we freely interchange the parameter indices with  $01234$ and $UBVRI$.)
The global parameters $\gamma^0$, $\gamma^1$  are the slopes that connect the extrinsic-color
parameters to observed magnitudes.

@@

\color{red}
Recall that our model does not specify the color of a supernova that suffers no extrinsic effects, but rather sets the
means of $k_0$ and $k_1$ to zero.
There are unconstrained $k_0^0$, $k_1^0$ that correspond to an intrinsic supernova.  The true extinction is
$A^T_X(k_0,k_1)= A_X(k_0,k_1) -  A_X(k^0_0,k^0_1)$ where $A_X(k_0,k_1) =  \gamma^0_X k_0 + \gamma^1_X k_1$.
The true color excess is $E^T(B-V) = A^T_B-A^T_V$.
Despite this ambiguity, a linear slope relating the $E^T(B-V)$ and $A^T_V$ for a set of supernova is the same slope
relating $A_V$ and $E(B-V)$.
\color{black}
Figure~\ref{avebv:fig} shows the relationship between $A_V$ and $E(B-V)$, from
which a linear fit gives a slope of $R_V=2.77^{+0.08}_{-0.09}$.
\color{red}
The full set of supernovae does not coincide with the expectations of a single linear law; the supernova population rather appears to be peaked
on a ridge line, with a tail distributed below.  That is, for a fixed color excess, the amount of $V$-band extinction is bounded above
but can have values that extend toward lower values.

The quantity $R^F_V = A^F_V/E^F(B-V)$ for an individual supernova is unspecified without knowledge of the intrinsic color.
For a qualitative view, we choose the zeros for $V$-band extinction and color-excess such that the bluest supernova roughly correspond to $E(B-V)=0$,
$A_V=0$, and such that the ridge line is close to constant.
With this ansatz, we
estimate $R^T_V$ per supernova shown in Figure~\ref{avebv:fig}, with the expectations of the
 \citetalias{1999PASP..111...63F} model for fixed $R^F_V$ overplotted.
With this choice of zeropoints, the ridge line corresponds to $R_V^F\lesssim 2.5$, and even lower values of $R_V^F$ below the ridge line.
We emphasize that the shape of the locus in this plot (though not the relative positions of the points)  and the flatness
of the ridge line is specific to our choice of zeropoints, and that our model does not specify the zeropoints.
A specification of per-supernova $R_V$ requires a model that can identify supernovae that suffer no extrinsic effects,
for example by modeling  a constraining distribution for the extrinsic parameters \citep{2016arXiv160904470M}.
\color{black}

@@

Until now we have considered $k_0$ and $k_1$ without association with any specific dust model, but they could be interpreted as
parameters of a single  dust model.
\color{red}
Plotted in Figure~\ref{avebv:fig} are the expectations for measured $A(V)$, $E(B-V)$, and $R^T_V$ for $R^F_V=1.1, 1.9, 2.5, 3.1$
within the context of the \citetalias{1999PASP..111...63F} model.
Note that for our broadband measurements, the relationship between $A(V)$ and $E(B-V)$ is subtly
non-linear, and $R^T_V$ is not constant for a fixed value of $R^F_V$.
\color{black}

The \citet{1989ApJ...345..245C} dust law can be expressed as a two-parameter linear model
\begin{equation}
A_X = a(X)  A_V + b(X) E(B-V).
\end{equation}
The \citet{1999PASP..111...63F} (hereafter referred to as \citetalias{1999PASP..111...63F}) model is approximately described by a linear model with
the above form, with
$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.78\}$ and $b(U,B,V,R,I)=\{  1.64,   1.06,   0.16,  -0.40,  -0.52\}$ for the case of
$R^F_V=2.5$
\color{red}
and $A^F_V=0.1$,
for the measurement of the updated
\citet{2007ApJ...663.1187H} SN~Ia template at $B$-band peak as seen through our synthetic passbands.
\color{black}
This linear approximation
is good in the ranges of
\color{red}
 $R^F_V$ and $A^F_V$,
\color{black}
and wavelengths under consideration, in that the values of the components  vary by $<5$\%.

Our model can be expressed as
\begin{equation}
A_X = \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V).
\end{equation}
\color{red}
Our median-fit values for the $\gamma$ coefficients,
$\frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2}  =\{4.78,   3.88,   2.88,   2.21,   1.59\}$ and
$ \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}=\{-3.85,   -4.69,   -5.69,  -5.33,  -4.77\}$,
\color{black}
can expressed in terms of the $a(X)$ and $b(X)$ vectors:
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} 
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
1.22 & 2.75 \\
0.81 & -5.50
\end{array}
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\begin{pmatrix}
\vec{\epsilon}_a \\
\vec{\epsilon}_b
\end{pmatrix},
\end{equation}
where the two residual $\vec{\epsilon}$ vectors are perpendicular to both $a(X)$ and $b(X)$ and
contribute  3\% and 4\% respectively to the total  length of the $\gamma$ vectors.
This result indicates that
the allowed variation of $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are almost identical.

@@

Data of SN~2014J are  analyzed using our model and using the parameter values found with the SNfactory sample.
The data for the color excesses  in $UBRi$  relative to $V$ at peak brightness  are taken from \citet{2014ApJ...788L..21A},
following their prescription of averaging measurements within 5-days of peak $B$ magnitude.
Their values 
$E_o(U-V) =   2.23 \pm   0.03$,
$E_o(B-V) =   1.28 \pm   0.04$,
$E_o(R-V) =  -0.47 \pm   0.03$,
$E_o(i-V) =  -0.92 \pm   0.03$
are plotted in Figure~\ref{sn2014j:fig}.
\color{red}
The central wavelengths of the filters are 3660, 4280, 5350, 6310, and 8100 \AA\ respectively, in contrast to the central
wavelengths 
3640, 4390, 5290, 6370, 7680 \AA\ of our synthetic bands.  Despite the imperfect correspondence our synthetic passbands
and those used for the observations,
\color{black}
these data are fit to our model
\begin{equation}
E_o(X-V) =  \left(\frac{\gamma^0_X}{\gamma^0_V}-1\right)x_0 +  \left(\frac{\gamma^1_X}{\gamma^1_V}-1\right)x_1,
\end{equation}
where we use the median values of the $\gamma$- and $\delta$-terms from Table~\ref{global:tab} and the fit
parameters $x_i $.

@@

The best-fit parameters for SN~2014J are 
%----
$x_0= 2.65$, $ x_1=-1.64$ with covariance
%----
\begin{equation}
\begin{pmatrix}
\begin{array}{rr}
0.048 & 0.047 \\
0.047 & 0.248
\end{array}
\end{pmatrix}.
\end{equation}
The predicted values of observed $E_o(B-V)$ from the fit are shown in Figure~\ref{sn2014j:fig}, where they are found to
overlap with the data within the error bars.   For comparison, the best-fit model determined by  \citet{2014ApJ...788L..21A} model using
UV through NIR data,
a  \citet{1999PASP..111...63F} dust with $R_V^F=1.4$ and $E(B-V)=1.37$
\color{red}
is shown in their Figure 3.
\color{black}
Our model predictions provide a significantly better match to the data
\color{red}
despite the only approximate correspondence of the model and observer passbands.
\color{black}

@@

\subsection{Improving SNe~Ia as Standard Candles}
The model and results presented here
carry information on the calibration of absolute magnitude.  The grey parameter $\Delta$ represents Hubble residuals after
application of the model, and its  $0.10$ mag dispersion has contributions from intrinsic dispersion, peculiar velocities, and
measurement uncertainties.
\color{red}
The purpose of this analysis was designed to mine information from the SNfactory data set, and so the results presented here
are specific to it both in terms of its population distribution and potentially noise.  This is the approach taken by previous
exploratory work.
A new analysis that explicitly measures out-of-sample performance is required to robustly determine how
well the addition of third parameter inferred from one data set can be used to measure supernova distances
of an independent set.
\color{black}
